\documentclass{scv}

\begin{document}

%-----------HEADER--------------
\resumeHeader{Sylee Beltiukov}{805-284-2410}{maybe.hello.world@gmail.com}{maybe-hello-world.github.io}{maybe-hello-world}{maybehelloworld}

%-----RESEARCH INTERESTS--------
\section{Research Interests}
    \justifying
    My current research lies at the intersection of networking and machine learning, especially network transformers and foundations models. 
    I am interested in developing credible ML-based artifacts and data representations for different networking and security problems, and democratizing network research by creating public measurement infrastructures, datasets, and tools.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingWithText
      {University of California, Santa Barbara}{Expected: August 2026}
      {Doctor of Philosophy (Ph.D.), Computer Science}{}
      {Advisor: Arpit Gupta.\\
        I have been working on democratizing networking research in the era of AI/ML and developing credible ML artifacts for networking problems.%
        Specifically, I have been working on fundamentally redesigning the ML pipeline for networking, enabling the development of credible and explainable ML models, diverse and representative network infrastructures to collect data from, and %
        creating large foundation models for network traffic.}{}
    \resumeSubheading
      {Peter the Great St.Petersburg Polytechnic University}{August 2019}
      {Master of Science (M.S.), Computer Science}{}
    \resumeSubheading
      {Peter the Great St.Petersburg Polytechnic University}{August 2017}
      {Bachelor of Science (B.S.), Computer Science}{}
  \resumeSubHeadingListEnd
    
%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading 
      {Graduate Research Assistant}{January 2021 -- Present}
      {University of California Santa Barbara}{Santa Barbara, California}
      \resumeItemListStart
        \resumeItem{Developed a high-quality pretrained transformer model working with network traffic data, \textit{netFound}~\cite{guthula2024netfoundfoundationmodelnetwork}, that produces high-quality embeddings for different network tasks.}
        \resumeItem{Developed a novel data-collection tool, \textit{netUnicorn}~\cite{beltiukov2023search}, that simplifies (iteratively) curating high-quality data for different learning problems from diverse network environments.}
        \resumeItem{Created a university-based network measurements infrastructure, \textit{PINOT}~\cite{beltiukov2023pinot}, that allows the collection of representative networking datasets from a real-world environment.}
        \resumeItem{Developed a model analysis tool, \textit{Trustee}~\cite{trustee} to identify underspecification issues in existing black box ML models.}
      \resumeItemListEnd
    
    \resumeSubheading 
      {Student Researcher}{June 2024 -- September 2024}
      {Google}{Sunnyvale, California}
      \resumeItemListStart
        \resumeItem{Developed a LLM-based approach for system logs analysis for hundreds of thousands of network devices in the Google production network.}
        \resumeItem{Proposed further research directions based on syslog analysis, including false positives identification, logs clusterization, and multi-step failure prediction.}
      \resumeItemListEnd

    \resumeSubheading 
      {On-Device Machine Learning Researcher}{March 2020 -- September 2021}
      {Huawei}{St.Petersburg, Russia}
      \resumeItemListStart
      \resumeItem{Developed and implemented a solution for the optimization of communication paths between smartphones and cloud services, that was deployed for pilot testing in China.}
      \resumeItem{Created a forward erasure correction code for data loss prevention optimized for mobile traffic and networks.}
      \resumeItem{Researched different congestion control protocols, such as BBR and internal company alternatives.}
      \resumeItem{Researched on-device ML model optimization and inference.}

    \resumeItemListEnd
      
    \resumeSubheading 
      {Junior Reinforcement Learning Researcher}{October 2019 -- June 2020}
      {JetBrains Research}{St.Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Reproduced and adapted several approaches to domain-specific tasks.}
        \resumeItem{Researched how to improve the usage of the Prioritized Experience Replay for World Models.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------PUBLICATIONS---------
\nocite{guthula2024netfoundfoundationmodelnetwork,beltiukov2023search,trustee,qfac,beltiukov2023pinot}
\resumePublications

% %---------Presentations---------
% \section{Invited Talks}
%   \resumeSubHeadingListStart
%   \resumeItemWithText
%   {In Search of netUnicorn: A Data-Collection Platform to Develop Generalizable ML Models for Network Security Problems}
%   {UC Santa Barbara (05/22), The University of Chicago (10/22), ACM SIGMETRICS Workshop on Measurements for Self-Driving Networks (06/23)}
%   \resumeSubHeadingListEnd

%----------AWARDS---------------
\section{Honors \& Awards}
  \resumeSubHeadingListStart
  \resumeSubSubheading{\textbf{Best Paper Honorable Mention}, IETF Applied Networking Prize}{2023}
  \resumeSubSubheading{\textbf{Winner}, UCSB CS Department Summer Fellowship Award}{2023}
  % \resumeSubSubheading{\textbf{Finalist}, Junction Hackathon, "Mobility Track", QOCO}{2018}
  \resumeSubSubheading{\textbf{Track Winner}, World IT Planet championship, Cloud Computing Track by Huawei}{2018}
  \resumeSubSubheading{\textbf{Special Award}, Institute of Bioinformatics, EPAM Systems}{2018}
  \resumeSubSubheading{\textbf{Track Winner}, World IT Planet championship, Cloud Computing Track by Huawei}{2017}
  % \resumeSubSubheading{\textbf{Challenge winner}, Junction Hackathon, "Robots and Learning Machines track", Eficode}{2017}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Selected Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{netFound}}{}
        \resumeItemListStart
          \resumeItem{netFound is a network traffic transformer model, allowing to utilize vast amount of unlabeled data to create powerful representations for different network tasks.}
          % \resumeItem{Provides abstractions and infrastructure interaction for developers of data collection pipelines and measurement experiments.}
          \resumeItem{Contribution: data processing, model and data scaling, training optimization, model dissection.}
          \resumeItem{Technologies: Python, Networking, LLM, Transformer models}
        \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{netUnicorn}}{}
          \resumeItemListStart
            \resumeItem{netUnicorn simplifies (iteratively) curating high-quality data for different learning problems from diverse network environments.}
            % \resumeItem{Provides abstractions and infrastructure interaction for developers of data collection pipelines and measurement experiments.}
            % \resumeItem{Contribution: system architecture, platform backend, team leading.}
            \resumeItem{Technologies: Python, REST API, PostgreSQL, Networking, Explainable AI}
            \resumeItem{Deployed in University of California, Santa Barbara and ETH Zurich}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{PINOT}}{}
          \resumeItemListStart
            \resumeItem{PINOT is a physical active measurement infrastructure deployed in the public university and provides a real-world view of the campus network.}
            % \resumeItem{Democratizes networking research by allowing researchers to easily collect diverse and representative datasets from a real user perspective.}
            \resumeItem{Contribution: system architecture, backend services, physical deployment, team leading.}
            \resumeItem{Deployed in University of California, Santa Barbara}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Trustee}}{}
          \resumeItemListStart
            \resumeItem{Decision tree -based framework for explainable AI in networking.}
            \resumeItem{Best Paper Honorable Mention \& IETF/IRTF Applied Networking Prize (ANRP)}
            \resumeItem{Contribution: public ML models dissection and verification, experiments reproducibility}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Technical Skills}
\resumeSkillListStart
  \resumeSkillItem{Machine Learning}{Classic Machine Learning, Time Series, Deep Learning, Explainable AI, PyTorch, Reinforcement Learning}
  \resumeSkillItem{Programming}{Python, Rust, SQL, C/C++, LaTeX}
  \resumeSkillItem{Other}{Computer Networks, Clouds (Azure, AWS, GCP), Docker, Linux (Debian-based) systems, Virtual Machines (Hyper-V, Xen), Databases, Spark, Git}
\resumeSkillListEnd

\section{Volunteering}
  \resumeSubHeadingListStart
  \resumeItemWithText
  {Queer Trans Community of University of California, Santa Barbara}
  {Events organizing, community building and moderation.}
  \resumeSubHeadingListEnd


\end{document}
